Extracting Angular Observables without a Likelihood\\and Applications to Rare Decays

### 2015-03-08 draft.tex
fixed small caption of the plots

\begin{figure}[t]
        \centering
            \includegraphics[width=0.45\textwidth]{figs/pull-Q2_5_6_S5_200.png}
            \includegraphics[width=0.45\textwidth]{figs/pull-Q2_5_6_S7_200.png}
        \caption{Pull distribution for the angular observables $S_5$ and $S_7$, extracted from $2\cdot 10^5$ studies of
        $200$ simulated events each for the decay $B\to K^*\ell^+\ell^-$. The red curve represents a fit to a gaussian distribution.}
        \label{fig:pulls}
\end{figure}

>>>>

\begin{figure}[t]
        \centering
            \includegraphics[width=0.45\textwidth]{figs/pull-Q2_5_6_S5_200.png}
            \includegraphics[width=0.45\textwidth]{figs/pull-Q2_5_6_S7_200.png}
        \caption{Pull distribution for the angular observables $S_5$ (left) and $S_7$ (right), extracted from $2\cdot 10^5$ studies of
        $200$ simulated events each for the decay $B\to K^*\ell^+\ell^-$. The red curve represents a fit to a gaussian distribution.}
        \label{fig:pulls}
\end{figure}
